A space-time \skewt model for threshold exceedances

### 2016-06-30 LaTeX/response.tex

\section*{Response to the comments of the Associate Editor}
\subsection*{Major comments}
\begin{enumerate}[1.]
\item The model in (1) has a non-standard skew distribution notation. As far as I could check, the parameter $\sigma^2$ should have an inverse gamma with parameters $a = b$, and not arbitrary and different $a$ and $b$. The equality is important in the derivations and it is one of the reasons we get $2a$ degrees of freedom. Indeed, some reserachers adopt $a/2$ and $a/2$ (rather than $a$ and $b$) such that they end up with a degrees of freedom. Can you provide a web-supplement proof that your more general model with $a \neq b$ is a skew-$t$ distribution with $2a$ degrees of freedom, or provide a reference for this result?\\

\begin{response}
  We have assumed that the errors $v(\bs)$ have unit variance, and $z \sim N(0, 1)$, so we require separate $a$ and $b$ so that $a$ can control the shape/degrees of freedom while $b$ controls the scale.
  Viewed this way, if $a = b$, then the degrees of freedom would determine the scale which is clearly too restrictive.
  To help clarify this, we have slightly modified the parameterization so that the degrees of freedom are $a$, and added additional clarification of the role of $b$ in \sref{sts:skewt}.
  We have also added \aref{sta:otherparams} to demonstrate our more general model with $a \neq b$ is a skew-$t$ distribution with $a$ degrees of freedom.
\end{response}

\item In the simulations, you adopted a prior distribution for the $a$ and $b$ parameters in $\sigma_t^2 (\bs) \sim IG(a, b)$ as $a \sim$ Gamma$(0.1, 0.1)$ and $b$ with a discrete distribution over a mesh from 0.1 to 10 with spacing $0.1$. The parameter $\sigma_t^2(\bs)$ is clearly a crucial parameter as it controls the scale. Why this choice? Trial and error? What have you used in the real dataset? Is this supposed to be a default choice?\\

\begin{response}
  In the original submission, the priors for $a$ and $b$ were inadvertently switched, so $a$ should have had a discrete distribution over a mesh from 0.1 to 10 with spacing $0.1$, and $b \sim$ Gamma$(0.1, 0.1)$.
  With the reparameterization given in the response to Major Comment 1, this actually means that the prior for $a$ is now a discrete distribution over a mesh from 0.2 to 20 with spacing $0.2$.
  As we now clarify in the specification of these priors both below equation \eref{steq:fullmodel} of the main text as well as in \sref{sts:simdesign} when describing the models we fit, $a$ is the degrees of freedom, and so this prior should be uninformative in all applications.
  In contrast, $b$ is a precision parameter, so its prior should be adapted to the scale of the response.
  In the real data analysis, we use the same discrete prior as in the simulation study, and find that for all settings in the cross validation, the posterior mean of $a$ is less than 3.
\end{response}

@@

  \begin{response}
    This has been corrected
  \end{response}

  \item Page 3, line -2: \ldots compared TO Gaussian AND max-stable \ldots \\

  \begin{response}
    This has been corrected
  \end{response}

  \item Page 8, line -1: a partition in the $\bw^*$ space induces a partition in the $\bw^*$. The property (7) is used in the $\bw^*$ space. Is this property still respected in the $\bw$ space since the transformation is non-linear and acts independently in each coordinate? \\

  \begin{response}
    As we now clarify in the final sentence of \sref{sts:temporal}, by construction the entire process including the prior on the partition is the same as the space-only model of \sref{sts:part}
    % \hl{Is this something we should be concerned about?}
  \end{response}

@@

  \begin{response}
    As we now describe at the end of the first paragraph of the introduction, two objectives for our data analysis are spatial prediction and mapping the probability of an extreme event.
    In the extremes context, spatial prediction means using the values of monitored stations to determine whether an unmonitored site experienced an extreme event.
    Mapping the probability of extreme events could either be the marginal probability of an event, such as ozone exceeding 75ppb, or a map of an upper quantile, such as the map of the 99th percentile in \fref{stfig:ozoneq99}.
  \end{response}

  \item There is a lot of confusion about the ``threshold'', and what this means in various contexts. Sometimes you discuss this as fixed and specified by regulation (e.g. p.3 l.5) but other times you refer to the role of censoring as not allowing low-moderate values influence the fit (e.g. Section 3.1 or the stated goal of modeling ``spatial extremes'' in the first line of Section 3) even though you state that the constant threshold is not extreme everywhere (e.g. in the Abstract, and p.15 l.3 where in fact the highest threshold you use in the application is the 0.06 quantile at some sites, and so hardly the tail!). The role of the threshold needs to be much more clearly explained in the context of the application (fixed thresholds of interest), and modeling the extremes. \\

  \begin{response}
    Yes, we can see how this could lead to confusion.
    In the revision, we now refer to the ``threshold'' as the value we select in the model-fitting process, i.e. $T$ in \sref{sts:censoring}.
    We also bolstered the description of the trade-off involved in selecting $T$ (see AE comment 4) in this section.
    As mentioned in the response to the previous comment, we also want to compute probabilities of extreme events (e.g. ozone exceeding 75ppb).
    We now refer to this as the probability above a high \emph{level}, $L$.
    That is, we might use the data above threshold $T = 50$ppb in order to estimate the probability of the response exceeding level $L = 75$ppb.
    Of course, this is only reasonable if $L \ge T$, and the user is free to select the $T$ that gives the best estimate of this probability.
  \end{response}

### 2016-06-30 LaTeX/skewt_rev.tex
edits to prepare for submitting the revision

\begin{abstract}
To assess the compliance of air quality regulations, the Environmental Protection Agency (EPA) must know if a site exceeds a pre-specified level.
In the case of ozone, the level for compliance is fixed at 75 parts per billion, which is high, but not extreme at all locations.
We present a new space-time model for threshold exceedances based on the spatial \skewt process.
Our method incorporates a random partition to permit long-distance asymptotic independence while allowing for sites that are near one another to be asymptotically dependent, and we incorporate thresholding to allow the tails of the data to speak for themselves.
We also introduce a transformed AR(1) time-series to allow for temporal dependence.
Finally, our model allows for high-dimensional Bayesian inference that is comparable in speed to traditional geostatistical methods for large datasets.
We apply our method to an ozone analysis for July 2005, and find that our model improves over both Gaussian and max-stable methods in terms of predicting exceedances of a high level.
\end{abstract}

@@

\section{Introduction}\label{sts:intro}
% In many climatological applications, researchers are interested in learning about the average behavior of different climate variables (e.g. ozone, temperature, rainfall).
Epidemiological studies have linked air quality to public health concerns regarding morbidity and mortality \citep{Samet2000}.
As a result, the Environmental Protection Agency (EPA) has developed a set of standards to help reduce air pollution thereby improving air quality.
Our study is motivated by an air pollution application where the focus is not on the average behavior, but instead the behavior over a high level determined by government regulation.
More specifically, we consider the case of compliance for ozone.
A site is said to be in compliance if the fourth highest daily maximum 8-hour concentration averaged over three years does not exceed 75 parts per billion (ppb).
\fref{stfig:ozone-10jul} shows the ozone levels from July 10, 2005, at 1089 stations across the United States.
We see a large area above the compliance level in the midwest covering Ohio, Indiana, Illinois, and parts of the surrounding states.
We analyze these data with the goals of spatial prediction for unmonitored locations and to map the probability of extreme events.

@@

Our approach differs from threshold modeling approaches based on extreme value distributions.
There has been extensive work on threshold modeling in the field of extreme value statistics where extreme events are naturally defined in terms of exceedances over a high threshold.
\citet{Davison1990} considered modeling threshold exceedances of univariate time series by the generalized Pareto distribution.
Threshold based inference for multivariate extreme value distributions was considered by \citet{Ledford1996} who introduced a censored approach that provides a way to deal with different types of exceedances of a threshold.
These threshold models were extended to spatial models for extremes by \citet{Wadsworth2012} and \citet{Thibaud2013} who fit various models to spatial extremes using a censored pairwise likelihood \citep{Padoan2010} based on the approach of \citet{Ledford1996}.
\citet{Huser2014} further extended this to space-time modeling.
\citet{Wadsworth2014}, \citet{Engelke2015}, and \citet{Thibaud2013a} introduced more efficient inference for threshold exceedances of extremal spatial processes with full likelihood methods.
The previous approaches to threshold modeling are motivated by extreme value theory and assume the threshold is high enough that extremal models are valid for the data, and for extrapolation beyond the range of observed values.
Moreover, these approaches are computationally intensive and limited to rather small datasets.
For example, \citet{Wadsworth2014} present a simulation study with observations at 16 sites on a regular grid, and \citet{Engelke2015} analyze a dataset with observations at 35 meteorological stations.
Our application with ozone data does not fit into this framework because we do not focus on exceedances of a very high level, and we have observations at over 1,000 ozone monitoring locations.

We propose a new spatiotemporal threshold exceedance model based on the \skewt process \citep{Padoan2011}.
We use a \skewt distribution because of its flexibility to model asymmetry and heavy-tailed data with the aim of predicting the probability of exceeding a high fixed level at an unobserved location.
Our model allows for inference and predictions using the full likelihood with computing on the order of Gaussian models.
This allows us to use Bayesian methods, which we use to fit the model, handle censored data below the threshold, and make predictions at unobserved locations.
The multivariate skew normal distribution was introduced by \citet{Azzalini1996}, and this was extended to the multivariate \skewt by \citet{Branco2001}.
These skew-elliptical distributions have been used in the spatial setting \citep{Genton2004,Kim2004}.
\citet{Zhang2010} propose the skew-Gaussian process as a class of stationary processes that have skewed marginal distributions.
\citet{Padoan2011} examined the usage of skew-Gaussian and \skewt distributions for multivariate extremes.
In a spatial setting, the multivariate \skewt distribution demonstrates asymptotic dependence between observations at all sites regardless of the distance between the sites.
In order to address this concern, we introduce a random spatial partition similar to the method used by \citet{Kim2005} for non-stationary Gaussian data.
This partitioning alleviates the asymptotic spatial dependence present in the \skewt distribution for sites that are far apart.

The paper is organized as follows.
\sref{sts:spatialskew} is a brief review of the spatial \skewt process.
In \sref{sts:spatial}, we build upon the traditional \skewt process by incorporating censoring to focus on tails, partitioning to remove long-range asymptotic dependence, and extending the model to space-time data.
The computing is described in \sref{sts:hier}.
In \sref{sts:simstudy}, we present a simulation study that examines the predictive capabilities of this model compared to Gaussian and max-stable methods.
We then compare our method to Gaussian and max-stable methods with a data analysis of ozone measurements from 1,000 sites throughout the US in \sref{sts:analysis}.
The final section provides brief discussion and direction for future research.

@@

\subsection{\Skewt process} \label{sts:skewt}
Let $Y(\bs)$ be a spatial process defined for spatial location $\bs$ in a spatial domain of interest $\calD \in \calR^2$.
The spatial \skewt process can be written as
\begin{align}
  Y(\bs) = \bX(\bs)^\top \bbeta + \lambda \sigma |z| + \sigma v(\bs) \label{steq:fullmodel}
\end{align}
where $\bX(\bs)$ is the observed covariate vector at site $\bs$, $\bbeta$ is the $p$-vector of regression parameters, $\lambda \in \calR$ is a parameter controlling skewness, $z \sim N(0, 1)$, $\sigma^2 \sim \text{IG}(a / 2, b / 2)$ is random scale parameter, IG is the distribution function of an inverse gamma random variable, $a$ is the degrees of freedom, $b$ controls the precision of the process, and $v(\bs)$ is a spatial Gaussian process with mean zero, variance one, and a positive definite correlation function $\text{Cor} \left[Y(\bs_1), Y(\bs_2)\right] = \rho(\bs_1, \bs_2)$.
Although any positive definite correlation function could be used, we choose to use the stationary isotropic \Matern correlation with
\begin{align}
  \rho(h) = (1 - \gamma) I(h = 0) + \gamma \frac{ 1 }{ \Gamma(\nu) 2^{ \nu - 1}} \left( \sqrt{2\nu} \frac{ h }{ \varphi } \right)^{\nu} K_{\nu} \left( \sqrt{2\nu} \frac{ h }{ \varphi } \right) \label{steq:matern}
\end{align}
where $I(\cdot)$ is an indicator function, $\varphi$ is the spatial range, $\nu$ is the smoothness, $\gamma$ is the proportion of variance accounted for by the spatial variation, $K_\nu$ is a modified Bessel function of the second kind, and $h = || \bs_1 - \bs_2 ||$ is the Euclidean distance between sites $\bs_1$ and $\bs_2$.

For a finite collection of locations $\bs_1, \ldots, \bs_n$, denote the vector of observations $\bY = [Y(\bs_1), \ldots, Y(\bs_n)]^\top$, and the covariate matrix $\bX_{n \times p} = [\bX(\bs_1), \ldots, \bX(\bs_n)]^\top$.
After marginalizing over both $z$ and $\sigma$, using the notation from \citet[p. 176]{Azzalini2014},
\begin{align} \label{steq:stazzalini}
  \bY \sim \text{ST}_n(\bX \bbeta, \bOmega, \balpha, a),
\end{align}
that is, $\bY$ follows an $n$-dimensional \skewt distribution with location $\bX \bbeta \in \calR^n$; covariance matrix $\bOmega_{n \times n} = \bomega \bar{\bOmega} \bomega$ where \mbox{$\bar{\bOmega}_{n \times n} = \frac{1}{1 + \lambda^2}(\bSigma + \lambda^2 \bOne \bOne^\top)$}, $\bSigma_{n \times n}$ is the positive definite correlation matrix which is obtained from $\rho(h)$, and $\bomega_{n \times n} = \text{diag}\left(\sqrt{\frac{ b }{a(1 + \lambda^2)}}, \ldots, \sqrt{\frac{ b }{a(1 + \lambda^2)}} \right)$; slant parameters $\balpha \in \calR^n = \lambda (1 + \lambda^2)^{1 / 2} (1 + \lambda^2 \bOne^\top \bSigma^{-1} \bOne)^{-1/2} \bSigma^{-1} \bOne$, and degrees of freedom $a$.
Furthermore, the marginal distributions at each location also follow a univariate \skewt distribution \citep{Azzalini2014}.
This process is desirable because of its flexible tail that is controlled by the skewness parameter and degrees of freedom.
% One major difference between the parameterization given in \eref{steq:fullmodel} and other parameterizations is that we characterize the skewnewss using $\lambda$ instead of the slant parameters $\balpha$.
For a comparison with other parameterizations, see \aref{sta:otherparams}.

@@

\subsection{Extremal dependence}\label{sts:extdep}
Our interest lies in spatial dependence in the tail of the \skewt process.
One measure of extremal dependence is the $\chi$ statistic \citep{Coles1999}.
For a stationary and isotropic spatial process, the $\chi$ statistic for locations $\bs_1$ and $\bs_2$ separated by distance $h = || \bs_1 - \bs_2 ||$ with identical marginal distributions is
\begin{align} \label{steq:chih}
  \chi(h) = \lim_{c \rightarrow c^*} \Pr[Y(\bs_1) > c | Y(\bs_2) > c]
\end{align}
where $c^*$ is the upper limit of the support of $Y$.
For the \skewt distribution, $c^* = \infty$.
If $\chi(h) = 0$, then observations are asymptotically independent at distance $h$.
For Gaussian processes, $\chi(h) = 0$ regardless of the distance $h$, so they are not suitable for modeling asymptotically dependent extremes.
Unlike the Gaussian process, the \skewt process is asymptotically dependent (the explicit expression for $\chi(h)$ is given in \aref{sta:skewt}).
However, one problem with the spatial \skewt process is that $\lim_{h \rightarrow \infty} \chi(h) > 0$.
This occurs because all observations, both near and far, share the same $z$ and $\sigma$ terms.
Therefore, this long-range dependence feature of the \skewt process is not desirable for spatial analysis of large geographic regions where we expect only local spatial dependence.
We propose a solution to this in \sref{sts:part}.

@@

\subsection{Censoring to focus on the tail} \label{sts:censoring}
As mentioned previously, we propose to use a censored approach because we do not want the low-to-moderate values to influence the fit of the overall model.
% The censored observations below the threshold give information on the marginal probabilities to exceed the threshold and on the dependence, but their values are not used to fit the model.
Let
\beq \label{steq:Yt}
  \widetilde{Y}(\bs) = \left\{ \begin{array}{ll}
      Y(\bs) \quad & \delta(\bs) = 1 \\
      T & \delta(\bs) = 0
  \end{array} \right.
\eeq
be the censored process at site $\bs$ where $Y(\bs)$ is the uncensored process, $\delta(\bs) = I[Y(\bs) > T]$, and $T$ is a pre-specified threshold value.
As our goal is to model exceedances above a high level $L$, we should select a value for $T \le L$.
For example, in predicting ozone exceedances, we might set $T = 50$ ppb in order to predict exceedances of $L = 75$ ppb.
Selecting $T$ too small may lead to bias in estimating the tail parameters; selecting $T$ too large increases variance.
We impute the censored values as a step in the algorithm used to fit the model described in \sref{sts:comp}, and use cross-validation to select $T$.

\subsection{Partitioning to remove long-range asymptotic dependence}\label{sts:part}
The motivation for the partition is that for a large spatial domain, it may not be reasonable to assume sites that are far apart demonstrate asymptotic dependence.
Modeling different levels of asymptotic dependence was discussed by \citet{Wadsworth2012}.
\citet{Huser2014} also allow for varying asymptotic dependence across both space and time with a partition structure represented by random discs moving across the space for a random duration with a random velocity and random radius.
We handle the problem of long-range asymptotic dependence with a random partition.
As discussed in \sref{sts:spatialskew}, the source of long-range dependence is the shared $z$ and $\sigma$.
Therefore, to alleviate this dependence, we allow $z$ and $\sigma$ to vary by site.
The model becomes
\begin{align} \label{steq:partition}
  Y(\bs) &= \bX(\bs)^\top \bbeta + \lambda \sigma(\bs) |z(\bs)| + \sigma(\bs) v(\bs).
\end{align}
To model spatial variation, consider a set of spatial knots $\bw_1, \ldots, \bw_K$ from a homogeneous Poisson process over spatial domain $\calD \in \calR^2$.
The knots define a random partition of $\calD$ by subregions $P_{1}, \ldots, P_{K}$ defined as
\begin{align} \label{steq:subregions}
  P_{k} = \{ \bs : k = \argmin_\ell || \bs - \bw_{\ell} || \}.
\end{align}
In other words, $P_k$ is composed of all sites for which the closest knot is $\bw_k$.
For all $\bs \in P_k$, with $k = 1, 2, \ldots, K$, the functions $z(\bs)$ and $\sigma(\bs)$ are equal to the constants $z_k$ and $\sigma_k$ respectively, and the $z_k$ and $\sigma^2_k$ are distributed as $z_k \iid N(0, 1)$ and $\sigma^2_k \iid$ IG$(a / 2, b / 2)$.
So, within each partition, $Y(\bs)$ follows the spatial \skewt process defined in \sref{sts:spatialskew}.
Across partitions, the $Y(\bs)$ remain dependence via the correlation function for $v(\bs)$ because $v(\bs)$ spans all partitions.
However, the bivariate distribution for sites in different partitions is neither Gaussian nor \skewt and does not have asymptotic dependence.

The partitioning model removes long-range dependence. Conditional on knots $\bw_1, \ldots, \bw_K$, the $\chi$ statistic for two sites $\bs_1$ and $\bs_2$ in partitions $k_1$ and $k_2$ respectively is
\begin{align}
  \chi(h) &= I(k_1 = k_2) \chi_{\text{skew-}t}(h) \label{steq:chiskewt}
\end{align}
where $\chi_{\text{skew-}t}(h)$ is the $\chi$ statistic for a \skewt process given in equation \eref{steq:chiskew-t} of \aref{sta:skewt}, and $h = ||\bs_1 - \bs_2||$.
Marginally, over the knots, $\chi(h) = \pi(h) \chi_{\text{skew}-t}(h)$, where \mbox{$\pi(h) = \Pr(k_1 = k_2)$} is the probability that two sites separated by distance $h$ are in the same partition.
In \aref{sta:proofsamepartition}, we show that $\lim_{h \rightarrow \infty} \pi(h) = 0$, assuming that the knots follow a homogeneous Poisson process.
This implies that $\lim_{h \rightarrow \infty} \chi(h) = 0$.
In practice we fix $K$ at a finite value and use a uniform distribution for the knots $\bw_1, \ldots, \bw_K$.
In \fref{stfig:chi}, we give $\chi(h)$ for $K = 1, 3, 5, 10$ partitions for a \skewt distribution with $\alpha = 10$, and 3 degrees of freedom.
In \fref{stfig:chi} we estimate $\pi(h)$ through simulation.
% To estimate $\pi(h)$, we generate 500 sites uniformly over the unit-square.
% We then randomly generate 400 different sets of partitions using $K = 3$, $5$, and $10$.
% For each set of knots, we take $\pi(h)$ to be the proportion of sites in the same partition that are separated by distance $h$.
% This plot demonstrates how partitioning helps to reduce extremal dependence as $h$ increases.

>>>>

\begin{abstract}
To assess the compliance of air quality regulations, the Environmental Protection Agency (EPA) must know if a site exceeds a pre-specified level.
In the case of ozone, the level for compliance is fixed at 75 parts per billion, which is high, but not extreme at all locations.
We present a new space-time model for threshold exceedances based on the \skewt process.
Our method incorporates a random partition to permit long-distance asymptotic independence while allowing for sites that are near one another to be asymptotically dependent, and we incorporate thresholding to allow the tails of the data to speak for themselves.
We also introduce a transformed AR(1) time-series to allow for temporal dependence.
Finally, our model allows for high-dimensional Bayesian inference that is comparable in computation time to traditional geostatistical methods for large datasets.
We apply our method to an ozone analysis for July 2005, and find that our model improves over both Gaussian and max-stable methods in terms of predicting exceedances of a high level.
\end{abstract}

@@

\section{Introduction}\label{sts:intro}
% In many climatological applications, researchers are interested in learning about the average behavior of different climate variables (e.g. ozone, temperature, rainfall).
Epidemiological studies have linked air quality to public health concerns regarding morbidity and mortality \citep{Samet2000}.
As a result, the Environmental Protection Agency (EPA) has developed a set of standards to help reduce air pollution thereby improving air quality.
Our study is motivated by an air pollution application where the focus is not on the average behavior, but on the behavior over a high level determined by government regulation.
More specifically, we consider the case of compliance for ozone.
A site is said to be in compliance if the fourth highest daily maximum 8-hour concentration averaged over three years does not exceed 75 parts per billion (ppb).
\fref{stfig:ozone-10jul} shows the ozone levels from July 10, 2005, at 1089 stations across the United States.
We see a large area above the compliance level in the midwest covering Ohio, Indiana, Illinois, and parts of the surrounding states.
We analyze these data with the goals of spatial prediction for unmonitored locations and to map the probability of extreme events.

@@

Our approach differs from threshold modeling approaches based on extreme value distributions.
There has been extensive work on threshold modeling in the field of extreme value statistics where extreme events are naturally defined in terms of exceedances over a high threshold.
\citet{Davison1990} considered modeling threshold exceedances of univariate time series by the generalized Pareto distribution.
Threshold based inference for multivariate extreme value distributions was considered by \citet{Ledford1996} who introduced a censored approach that provides a way to deal with different types of exceedances of a threshold.
These models were extended to spatial models for threshold exceedances by \citet{Wadsworth2012} and \citet{Thibaud2013} who fit various models to spatial extremes using a censored pairwise likelihood \citep{Padoan2010} based on the approach of \citet{Ledford1996}.
\citet{Huser2014} further extended this to space-time modeling.
\citet{Wadsworth2014}, \citet{Engelke2015}, and \citet{Thibaud2013a} introduced more efficient inference for threshold exceedances of extremal spatial processes with full likelihood methods.
The previous approaches to threshold modeling are motivated by extreme value theory and assume the threshold is high enough that extremal models are valid for the data and for extrapolation beyond the range of observed values.
Moreover, these approaches are computationally intensive and limited to rather small datasets.
% For example, \citet{Wadsworth2014} present a simulation study with observations at 16 sites on a regular grid, and \citet{Engelke2015} analyze a dataset with observations at 35 meteorological stations.
Our application with ozone data does not fit into this framework because we do not focus on exceedances of a very high level, and we have observations at 1,089 ozone monitoring locations.

We propose a new spatiotemporal threshold exceedance model based on the \skewt process \citep{Padoan2011}.
We use a \skewt distribution because of its flexibility to model asymmetry and heavy-tailed data with the aim of modeling exceedances of a high fixed level at an unobserved location.
Our model allows for inference and predictions using the full likelihood with computing on the order of Gaussian models.
This allows us to use Bayesian methods, which we use to fit the model, handle censored data below the threshold, and make predictions at unobserved locations.
The multivariate skew normal distribution was introduced by \citet{Azzalini1996}, and this was extended to the multivariate \skewt by \citet{Branco2001}.
These skew-elliptical distributions have been used in the spatial setting \citep{Genton2004,Kim2004}.
\citet{Zhang2010} propose the skew-Gaussian process as a class of stationary processes that have skewed marginal distributions.
\citet{Padoan2011} examined the usage of skew-Gaussian and \skewt distributions for multivariate extremes.
In a spatial setting, the multivariate \skewt distribution demonstrates asymptotic dependence between observations at all sites regardless of the distance between the sites.
In order to address this concern, we introduce a random spatial partition similar to the method used by \citet{Kim2005} for non-stationary Gaussian data.
% This partitioning alleviates the asymptotic spatial dependence present in the \skewt distribution for sites that are far apart.

The paper is organized as follows.
\sref{sts:spatialskew} is a brief review of the spatial \skewt process.
In \sref{sts:spatial}, we build upon the traditional \skewt process by incorporating censoring, partitioning, and extending the model to space-time data.
The computing is described in \sref{sts:hier}.
In \sref{sts:simstudy}, we present a simulation study that examines the predictive capabilities of this model compared to Gaussian and max-stable methods.
We compare our method to Gaussian and max-stable methods with a data analysis of ozone measurements throughout the US in \sref{sts:analysis}.
% The final section provides brief discussion and direction for future research.

@@

\subsection{\Skewt process} \label{sts:skewt}
Let $Y(\bs)$ be a spatial process defined for spatial location $\bs$ in a spatial domain of interest $\calD \in \calR^2$.
The spatial \skewt process can be written as
\begin{align}
  Y(\bs) = \bX(\bs)^\top \bbeta + \lambda \sigma |z| + \sigma v(\bs) \label{steq:fullmodel}
\end{align}
where $\bX(\bs)$ is the observed covariate vector at site $\bs$, $\bbeta$ is the $p$-vector of regression parameters, $\lambda \in \calR$ is a parameter controlling skewness, $z \sim N(0, 1)$, $\sigma^2 \sim \text{IG}(a / 2, b / 2)$ is random scale parameter, IG is the distribution function of an inverse gamma random variable, $a$ is the degrees of freedom, $b$ controls the precision of the process, and $v(\bs)$ is a standard Gaussian process with positive definite correlation function $\text{Cor} \left[Y(\bs_1), Y(\bs_2)\right] = \rho(\bs_1, \bs_2)$.
Although any positive definite correlation function could be used, we choose to use the stationary isotropic \Matern correlation with
\begin{align}
  \rho(h) = (1 - \gamma) I(h = 0) + \gamma \frac{ 1 }{ \Gamma(\nu) 2^{ \nu - 1}} \left( \sqrt{2\nu} \frac{ h }{ \varphi } \right)^{\nu} K_{\nu} \left( \sqrt{2\nu} \frac{ h }{ \varphi } \right) \label{steq:matern}
\end{align}
where $I(\cdot)$ is an indicator function, $\varphi > 0$ is the spatial range, $\nu > 0$ is the smoothness, $\gamma \in [0, 1]$ is the proportion of variance accounted for by the spatial variation, $K_\nu$ is a modified Bessel function of the second kind, and $h = || \bs_1 - \bs_2 ||$ is the Euclidean distance between sites $\bs_1$ and $\bs_2$.

For a finite collection of locations $\bs_1, \ldots, \bs_n$, denote the vector of observations $\bY = [Y(\bs_1), \ldots, Y(\bs_n)]^\top$, and the covariate matrix $\bX_{n \times p} = [\bX(\bs_1), \ldots, \bX(\bs_n)]^\top$.
After marginalizing over both $z$ and $\sigma$, using the notation from \citet[p. 176]{Azzalini2014},
\begin{align} \label{steq:stazzalini}
  \bY \sim \text{ST}_n(\bX \bbeta, \bOmega, \balpha, a),
\end{align}
that is, $\bY$ follows an $n$-dimensional \skewt distribution with location $\bX \bbeta \in \calR^n$; covariance matrix $\bOmega_{n \times n} = \bomega \left[ \frac{1}{1 + \lambda^2}(\bSigma + \lambda^2 \bOne \bOne^\top) \right] \bomega$, $\bSigma_{n \times n}$ is the positive definite correlation matrix which is obtained from $\rho(h)$, and $\bomega_{n \times n} = \text{diag}\left(\sqrt{\frac{ b }{a(1 + \lambda^2)}}, \ldots, \sqrt{\frac{ b }{a(1 + \lambda^2)}} \right)$; slant parameters $\balpha \in \calR^n = \lambda (1 + \lambda^2)^{1 / 2} (1 + \lambda^2 \bOne^\top \bSigma^{-1} \bOne)^{-1/2} \bSigma^{-1} \bOne$, and degrees of freedom $a$.
Furthermore, the marginal distributions at each location also follow a univariate \skewt distribution \citep{Azzalini2014}.
This process is desirable because it is heavy tailed with tail index $a$, and the shape of the distribution is controlled by the skewness parameter.
% One major difference between the parameterization given in \eref{steq:fullmodel} and other parameterizations is that we characterize the skewnewss using $\lambda$ instead of the slant parameters $\balpha$.
For a comparison with other parameterizations, see \aref{sta:otherparams}.

@@

\subsection{Extremal dependence}\label{sts:extdep}
Our interest lies in spatial dependence in the tail of the \skewt process.
One measure of extremal dependence is the $\chi$ statistic \citep{Coles1999}.
For a stationary and isotropic spatial process, the $\chi$ statistic for two locations separated by distance $h$ is
\begin{align} \label{steq:chih}
  \chi(h) = \lim_{c \rightarrow c^*} \Pr[Y(\bs + h) > c | Y(\bs) > c]
\end{align}
where $c^*$ is the upper limit of the support of $Y$; for the \skewt distribution $c^* = \infty$.
If $\chi(h) = 0$, then observations are asymptotically independent at distance $h$.
For Gaussian processes, $\chi(h) = 0$ regardless of the distance $h$, so they are not suitable for modeling asymptotically dependent extremes.
Unlike the Gaussian process, the \skewt process is asymptotically dependent (the explicit expression for $\chi(h)$ is given in \aref{sta:skewt}).
However, one problem with the spatial \skewt process is that $\lim_{h \rightarrow \infty} \chi(h) > 0$.
This occurs because all observations, both near and far, share the same $z$ and $\sigma$ terms.
Therefore, this long-range dependence feature of the \skewt process is not desirable for spatial analysis of large geographic regions where we expect only local spatial dependence.
We propose a solution to this in \sref{sts:part}.

@@

\subsection{Censoring to focus on the tail} \label{sts:censoring}
We do not want the low-to-moderate values to influence the fit of the model.
We propose the use of a censored approach to fit threshold exceedances only.
More specifically, we assume our \skewt model $Y(\bs)$ is valid at each location $\bs$ above a threshold $T$, and censor the values below $T$ for which we don't assume the model to be valid.
We define our partially censored observations as $\widetilde{\bY} = [\widetilde{Y}(\bs_1), \ldots, \widetilde{Y}(\bs_n)]^\top$ where $\widetilde{Y}(\bs) = \max\{Y(\bs), T\}$, and fit the \skewt process to these $\widetilde{\bY}$.
In our Bayesian framework, inference can be easily performed by imputing censored observations below $T$ (see \sref{sts:comp}).
% We propose to use a censored approach because we do not want the low-to-moderate values to influence the fit of the model.
% % The censored observations below the threshold give information on the marginal probabilities to exceed the threshold and on the dependence, but their values are not used to fit the model.
% % \beq \label{steq:Yt}
% %   \widetilde{Y}(\bs) = \left\{ \begin{array}{ll}
% %       Y(\bs) \quad & \delta(\bs) = 1 \\
% %       T & \delta(\bs) = 0
% %   \end{array} \right.
% % \eeq
% We will assume our data were generated from the censored process $\widetilde{Y}(\bs) = \max\{Y(\bs), T\}$ where $T$ is a pre-specified threshold value.
% Then from the censored process, the vector of observations becomes $\widetilde{\bY} = [\widetilde{Y}(\bs_1), \ldots, \widetilde{Y}(\bs_n)]^\top$.

As our goal is to model exceedances above a high level $L$, we should select a value for $T \le L$.
For example, in predicting ozone exceedances, we might set $T = 50$ ppb in order to predict exceedances of $L = 75$ ppb.
Selecting $T$ too small may lead to bias in estimating the tail parameters; selecting $T$ too large increases variance.
We impute the censored values as a step in the algorithm used to fit the model described in \sref{sts:comp}, and use cross-validation to select $T$.

\subsection{Partitioning to remove long-range asymptotic dependence}\label{sts:part}
For a large spatial domain, it may not be reasonable to assume sites that are far apart demonstrate asymptotic dependence.%, so we handle the problem of long-range asymptotic dependence with a random partition.
% Modeling different levels of asymptotic dependence was discussed by \citet{Wadsworth2012}.
% \citet{Huser2014} also allow for varying asymptotic dependence across both space and time with a partition structure represented by random discs moving across the space for a random duration with a random velocity and random radius.
As discussed in \sref{sts:spatialskew}, the source of long-range dependence is the shared $z$ and $\sigma$.
Therefore, to alleviate this dependence, we allow $z$ and $\sigma$ to vary by site using a partitioning approach.
The model becomes
\begin{align} \label{steq:partition}
  Y(\bs) &= \bX(\bs)^\top \bbeta + \lambda \sigma(\bs) |z(\bs)| + \sigma(\bs) v(\bs).
\end{align}
To model spatial variation, consider a set of spatial knots $\bw_1, \ldots, \bw_K$ from a homogeneous Poisson process over spatial domain $\calD \in \calR^2$.
The knots define a random partition of $\calD$ by subregions $P_{1}, \ldots, P_{K}$ defined as
\begin{align} \label{steq:subregions}
  P_{k} = \{ \bs : k = \argmin_\ell || \bs - \bw_{\ell} || \}.
\end{align}
In other words, $P_k$ is composed of all sites for which the closest knot is $\bw_k$.
For all $\bs \in P_k$, with $k = 1, 2, \ldots, K$, the functions $z(\bs)$ and $\sigma(\bs)$ are equal to the constants $z_k$ and $\sigma_k$ respectively, and the $z_k$ and $\sigma^2_k$ are distributed as $z_k \iid N(0, 1)$ and $\sigma^2_k \iid$ IG$(a / 2, b / 2)$.
So, within each partition, $Y(\bs)$ follows the spatial \skewt process defined in \sref{sts:spatialskew}.
Across partitions, the $Y(\bs)$ remain dependent via the correlation function for $v(\bs)$ because $v(\bs)$ spans all partitions.
However, the bivariate distribution for sites in different partitions is neither Gaussian nor \skewt and does not have asymptotic dependence.
